\documentclass[11pt,a4paper]{article}

% --- Common Packages across layouts --- %
\usepackage{microtype}
\usepackage{graphicx}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{todonotes}
\usepackage{dirtytalk}
\usepackage{siunitx}
\usepackage{xspace}
\usepackage{lipsum} % For testing

%\usepackage{allrunes} package allrunes to add, but currently unstable due to trying to redefine \swdefault and \dot



% Article and report specific packages %

% Visual style packages

\usepackage[margin = 2.5cm]{geometry}
\usepackage{wrapfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[nocheck]{fancyhdr}
\usepackage{titlesec}
\usepackage{blindtext}
\usepackage{enumitem}
\setitemize{itemsep=2pt, topsep=4pt, parsep=4pt, partopsep=6pt}

% Maths / Science packages
\usepackage{amsfonts, amssymb, amsmath, amsthm}
\usepackage{bm}
\usepackage{physics}
\usepackage{tikz}
\usepackage{circuitikz}
\usepackage{cancel}
\usepackage{mathrsfs} % New font family from \mathscr{}

% Other utility packages
\usepackage{multicol}
\usepackage{afterpage}
\usepackage[backend=biber, style=numeric]{biblatex}
\addbibresource{references.bib}



% My (John's) personal utility packages
\usepackage{packages/johns-package-setup}
\usepackage{packages/johns-preferences}


% ============================================ %
%    ARTICLE / SHORT REPORT TEMPLATE         %
% ============================================ %

% Article/short report template specific tweaks -- consider turning into a new (conditional) package
\numberwithin{equation}{section}

% Setting up headers and footers for fancyhf
\fancyhf{}
\fancyhead[R]{\today}
\fancyhead[L]{Project Overview}
\fancyfoot[C]{\thepage}
\headsep = 15pt
\voffset = 10pt

% Title and introduction to the report
\title{Project Overview}
\author{John Perry\thanks{Churchill College}}
\date{\today}

\begin{document}

\pagestyle{empty}
\newgeometry{margin = 2cm}
\pagenumbering{arabic}

\maketitle

% Set headers and footers to exist past the title page
% \afterpage{\thispagestyle{fancy}} % Was useful when not dealing with multicol
\pagestyle{fancy}

\begin{abstract}
    % Give the abstract of the document with the reason it exists, the significance of its contribution to the project and the conclusions it provides.
    Document containing the overview of the plans and goals of the Custom Split Keyboard project. First, the different kinds of property desired from the keyboard are listed with a brief summary of each, then following that a more in-depth analysis of each property is given.
\end{abstract}

\section{Introduction}
% Introduce the problem, and contextualise it and the objectives of the experiment/thing being reported on
I currently feel like the keyboards I have don't fully meet my needs practically. Key things include:
\begin{itemize}
    \item More optimised/better battery life.
    \item More portable so it can be taken round different places more easily.
    \item More comfortable for the work I want to do with it.
\end{itemize}

\subsection{Objectives}

The different objectives for the finished keyboard include:
\begin{itemize}
    \item \SI{80}{\percent}:\footnote{Or smaller? It should be investigated if I am comfortable with using layers \textit{if} they are comfortable for me.} I want a keyboard that is not too large.
    \item \textbf{Ortholinear}: Partly that I want to try it out, but also it is meant to be very comfy.
    \item \textbf{Custom layout}: I want to have a comfy layout that is much nicer for coding but also not too dissimilar from QWERTY because I realise that simply fully going away from the norm will be a massive pain to learn again.\footnote{Consider how much more I can use my thumbs for, as just on the spacebar is a waste!}
    \begin{itemize}
        \item Additionally, it would be good to have a \textit{flexible} layout as well. I want to be able to change my opinions on the locations of different keys and experiment.
    \end{itemize}
    \item \textbf{Split layout}: For ergonomics I want to try out a split layout, but I also want to be able to connect the two sides in a robust way to make a single keyboard (that also looks sleek) if wanted.\footnote{If I can connect the two sides with pogo pins that would be quite cool.}
    \item \textbf{Low profile}: Currently I don't have any low profile keyboard, and it would be cool to have something that is more portable and practical to use.
    \item \textbf{Top-of-the-line switches}: I might want to be able to use the keyboard for gaming, so top-tier switches would be preferable.
    \item \textbf{Compact and portable}: I want to be able to pack and move the keyboard easily, to actually make it feel good to use and that I would want to take it with me.
    \item \textbf{Good battery}: Since the battery is a point where many keyboards seem to make a compromise and cut corners, I want the battery life to be exceptional even in a small chassis.
    \item \textbf{Nice feeling materials}: I want the keyboard to \textit{feel} premium. That means ceramic-like keycaps, metal (or high-quality plastic) frame, and nice rubber feet to make it feel sleek and premium.
    \item \textbf{Good sound/acoustics}: I want it to feel nice to use, so it should have the capability to sound good---using nice materials and including space for sound dampening/adjustment.
\end{itemize}

\section{Custom layout}

\begin{itemize}
    \item Use my thumbs for more! What would be good to have on my thumbs would be commonly used coding symbols/buttons to press. For example:
    \begin{itemize}
        \item \textit{Enter} key: When writing code, it is very inconvenient to move fingers to press enter. It is also very on-theme.
        \item \textit{Brackets/braces}: Different brackets and braces (e.g. [ ], \{ \}, ( )) would be good to have on thumbs. Particularly having the opening ones on my left and closing on my right would feel quite nice I'd imagine.
    \end{itemize}
    \item Relocating \say{home} and \say{end} might actually work well in a workflow if I get in the right patterns.
    \item As well as pure coding, it would be nice to have 
\end{itemize}

\end{document}